Debugging of RxJS-based Applications

### 2020-10-02 paper.tex
Fix Rendering
Add Co-Author

@@

rxjs-playground renders all observables\' values and life cycles in real-time allowing quick iteration on a specific piece of code.

@@

\begin{acks}
	We want to thank the engineers who participated in our study for their time. Further, we would like to thank Prof. Dr. Markus Stolze for his mentorship and many tireless review sessions.
\end{acks}

>>>>

\author{Prof. Dr. Markus Stolze}
\affiliation{
	\institution{Eastern Switzerland University of Applied Sciences}
	\city{Rapperswil}
	\country{Switzerland}
}
\email{markus.stolze@ost.ch}

@@

rxjs-playground renders the values and life cycle events for all observables in real-time, allowing quick iterations on a specific piece of code.

@@

\begin{acks}
	We want to thank the engineers who participated in our study for their time.
\end{acks}
